Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-06-13 Manuscript/proto-manuscript.tex
New intro and other updates

\begin{abstract}
% insert abstract here
Classical molecular dynamics simulations give detailed information about membrane structure and dynamics. 
However, there is still a room for improvements in current force fields – it is known from the literature, that the binding of ions, especially cations, to phopholipid membranes is overestimated in all classical models [1]. 
We suggest that the membrane-ion interactions can be corrected by including implicit electronic polarizability into the lipid models through the electronic continuum correction (ECC) [2], which was already applied to monovalent and divalent ions yielding models that feature correct ion pairing [3]. 
Using the electrometer concept [3, 4] and x-ray scattering form factors, our simulations point out that our hypothesis is correct and ECC is indeed a missing important contribution in current classical lipid models. 
Moreover, the solid physical principles behind ECC are found not to hamper other relevant properties of a phospholipid bilayer. 
The new lipid model, "ECC-lipids", shows accurate binding affinity to sodium and calcium cations and headgroup order parameter response to bound charge. 
We also provide for the first time a realistic stochiometry of bound calcium cations to a POPC membrane, and their binding sites. 
This work will continue as an open collaboration project NMRlipids IV (http://nmrlipids.blogspot.fi).

[1] Catte, A., Girych, M., Javanainen, M., Melcr J., Miettinen, M. S., Oganesyan, V. S. and Ollila H. S.,  PCCP 18(47) 32560-32569 (2016)
[2] Leontyev, I. V., and Stuchebrukhov, A. A., JCTC 6(5) 1498–1508 (2010)
[3] Kohagen, M., Mason, P. E., and Jungwirth, P., J. Phys. Chem. B 120(8) 1454–60 (2015)
[4] Seelig, J., MacDonald, P. M., and Scherer, P. G., Biochemistry 26(24) 7535–7541 (1987)
\end{abstract}

@@

% Here I write pseudo-article statements that will make the main argument.
% Beautiful polished sentences will be formed only afte we agree on these basic things
\section{Introduction}

 motivation, significance of membranes, phospholipids and simulation.

 assumptions (so that we have structure of the paper like in a mathematical proof) -- 
 MD simulation is a good tool for studying molecules.
 classical MD models can describe lipids accurately,

 MD is ... and it serves ... it is useful for ... (describe throuhg references)

 Lipid membranes, especially phospholipid membranes; their significance for life, sciences, society, pharma ...

%\textbf{Specific introduction: current FFs and MDEC/ECC}

 Current force fields -- pros and cons, at a good shape in many aspects, agree on various properties.  -- write basic ideas from the lipid-FF whitepaper I did recently.

 lipid force fields fail in description of membrane-cation interaction -- could be answered by ECC? 
Cations were shown to generally overbind in PC lipid bilayers in NMRlipids II project. 
Here we propose that the cation overbinding can be corrected by implicitly inducing electronic polarizability in lipid headgroups by scaling the partial charges -- i.e. MDEC/ECC~\cite{leontyev11}\todo{Bulid BibTex references database.} paradigm.

MDEC -- or -- ECC 
\todo{choose one}{We have to decide whether we will refer to the method as a correction (ECC) or as a MD simulation paradigm (MDEC) -- and choose on of these labels. -- Joe: use ECC as we apply MDEC rather as a correction to current state not as a new paradigm for FF development.}
MD in electronic continuum as in \cite{leontyev11} or electronic continuum correction as in \cite{Jungwirth2015}

Describe ECC: good physical concept for treating part of the polarizability (electronic) in a simple mean-field way.

Succesful application: Works for cations \cite{Jungwirth2015,kohagen14,kohagen16}\todoii{REF}{Missing references} -- motivation for its application to zwitterionic lipids like POPC.

Hypothesis: ECC helps in describing even zwitterionic molecules like POPC, will be demonstrated through headgroup order parameter response to cationic molecules.

To date, there is no lipid model that can describe such a behaviour, 
the electrometer response and cation binding, quantitatively well~\cite{catte16}

Almost all lipid bilayer simulations reported in the literature 
are done with force fields that represent interactions between atoms
with pairwise additive empirical potential and exclude the electronic 
polarizability \cite{SOME_review, FF_papers}. While the issue has been 
considered higly relevant since the early days of lipid bilayer simulations,
practical solutions have turned out to be complicated \cite{??}.
Here we propose that electronic polarizability can be effectively included
in lipid bilayer simulations by using the electronic contimuun correction \cite{leontyev11}.

@@

\subsection{Lipid bilayers without ions}
The scattering form factors, NMR order parameters and area per lipids calculated from 
the ECC corrected lipid model for POPC are compared to experiments and original
Lipid14 results in Fig. \ref{simVSexpNOions} and in Table~\ref{tab:apls}. 
%The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
%by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.
The structural quality is comparable to the state of art lipid models available in literature \cite{ollila16},
thus we conclude that the ECC corrected lipid model reproduces the lipid bilayer structure
in liquid disordered phase with similar accuracy than other available models
\todo{Discussion to be finished when we have all the results in the figure}.

Headgroup order parameter response to bound charge was evaluated against
experimental data measured with cationic surfactant
(dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$) \cite{scherer89}.
The exact amount of bound charge in the membrane is known these systems, because
practically all cationic surfactant molecules are embedded in lipid bilayer due to
their amphiphilic nature. Thus, the headgroup order parameter changes as a function of
mole fraction of cationic surfactants in  Fig. \ref{OrderParameterCHANGESnewMODELS} gives
also the order parameter changes as a function of bound cations.
\todo{I think that we should make a separate figure for this one and ion concentrations.
  In the current figure it would be difficult to show this with a reasonable scale.
  Currently Lipid14 results are cut out, thus the scale should be increased.
  This would, however, make the changes with CaCl too small.
  The change of headgroup tilt could be incorporated in the same figure with order parameter
  response to cationic surfactant.
}
The headgroup order parameter response to bound cation concentration
is approximately linear up to $\sim$0.3 mole fraction in experiments \cite{scherer89}.
The linearity is also observed in simulations with original Lipid14 and with ECC correction.
%from experiments \cite{seelig87} and simulations with Lipid14 model and with ECC-lipids model 
%as a function of bound charge are shown in
Quantitative comparison, however, reveals that the response is overestimated in 
original Lipid14 for both segments, while the ECC corrected model gives a
good agreement for the change of $\alpha$ segment order parameter, but slightly
underestimates the $\beta$ segment order parameter change.
The overestimation of order parameter changes with original Lipid14 model 
suggests that the overestimated response with CaCl$_2$ concentration in \cite{catte16} 
can be partly explained by the high sensitivity of the headgroup order parameter response
to bound charge.

Secondly, the $S^\alpha/S^\beta$ ratio of the response is found to be slightly larger than in 
experiments (VALexp vs VALsim
\todo{Add values of $S^\alpha/S^\beta$ response for sim and experiment
  SAMULI: Maybe these could be put in the same figure with the order parameter
  response and P-N vector angle change with surfactants.
}
).
This property is kept also by the newly derived model, ECC-lipid, and, hence, 
it shows a perfect agreement in the response of the headgroup order parameter $S^\alpha$ 
but underestimates slightly the response of $S^\beta$. 
\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
%  \caption{\label{fig:form-f}
%    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
%\end{figure}
%
%\begin{figure}[]
%  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and EECLipid17 models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure}
  \todo{Should we add the results from original lipid14?}
\end{figure}
Area per molecules extracted from MD simulations and SPD model fitted to scattering data \todo{check that this the case for the used values}
are shown in Table \ref{tab:apls}.
\todo{finalize figure (NMR headgr. OPs + SAXS, continue in the discussion.}
\begin{table}
  \caption{Area per lipid from different models for POPC without ions\label{tab:apls} }
  \begin{tabular}{c c c}
    model          & A (Å$^2$)   & Temperature [K] \\
    \hline
    Lipid14 (literature)  & 65.6$\pm$ 0.5  &  303 \\
    Lipid14ecc0.80+sigma0.875 &        &  313    \\
    GMX small patch           & 64.9   &         \\
    GMX 4xbig patch           & 65.5   &         \\
    oMM small patch           & 63.65  &         \\
    oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment \cite{Jambeck2012}\todoii{REF}{put original references, not Slipids param. paper.}  & 62.7  &  293    \\
    experiment  & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2_surf.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of NaCl, CaCl$_2$ concentration and
    cationic surfactant (dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$)
    from simulations and experiments (DPPC \cite{akutsu81}, POPC \cite{altenbach84}, surfactant \cite{scherer89}).
    Simulations with Lipid14 and Åqvist ion model from \cite{catte16,lipid14POPC0mMNaClfiles,lipid14POPC350mMCaClfiles,lipid14POPC1000mMCaClfiles}.
  }
  \todoii{Add Lipid14-Aquist data.}{Lipid14/Åqvist data to be added from https://github.com/NMRLipids/lipid\_ionINTERACTION/blob/master/Data/POPC/CaCl/LIPID14/LIPID14caclCONSchange.dat . Joe: I'm not sure what is meant -- I think Aquist data are actually plotted there. I recently changed it to L14+Dang ions (both data and plot). I think just one ion model is sufficient (and ECC-ions are based on Dang model).}
\end{figure*}

Ion density profiles between different simulation models are compared in Fig. \ref{fig:cacl-dens}.
Density profiles from simulations with original Lipid14 and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{kohagen14,kohagen16} along with original Lipid14 does not significantly change it. 
The new ECC-lipid model with scaled ions exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
This demonstrates how importnat it is to account for electronic polarizability also in molecules with zero total charge. 
Alltogether,
the response of headgroup order parameters as a function of CaCl$_2$ concentration is in agreement with
experiments in the new ECC-lipid model simulated with ECC model of CaCl$_2$. 
This is a significant improvement
over previous models available for lipid--ion interactions studies \cite{catte16} and indicates that
the new model can be used for detailed studies of lipid-ion interactions.

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Aquist parameters and with ECC ions and ECCLipids17 with ECC ions. }
\end{figure}

@@

not only due to overestimated binding of cations.

>>>>

\begin{abstract}
  % insert abstract here
  \todo{Abstract directly from Joe's conference abstracts. To be rewritten.}
Classical molecular dynamics simulations give detailed information about membrane structure and dynamics. 
However, there is still a room for improvements in current force fields – it is known from the literature,
that the binding of ions, especially cations, to phopholipid membranes is overestimated in all classical models [1]. 
We suggest that the membrane-ion interactions can be corrected by including implicit electronic polarizability into the
lipid models through the electronic continuum correction (ECC) [2], which was already applied to monovalent and divalent
ions yielding models that feature correct ion pairing [3]. 
Using the electrometer concept [3, 4] and x-ray scattering form factors, our simulations point out that our hypothesis is
correct and ECC is indeed a missing important contribution in current classical lipid models. 
Moreover, the solid physical principles behind ECC are found not to hamper other relevant properties of a phospholipid bilayer. 
The new lipid model, "ECC-lipids", shows accurate binding affinity to sodium and calcium cations and headgroup order parameter response to bound charge. 
We also provide for the first time a realistic stochiometry of bound calcium cations to a POPC membrane, and their binding sites. 
This work will continue as an open collaboration project NMRlipids IV (http://nmrlipids.blogspot.fi).
\end{abstract}

@@

% Here I write pseudo-article statements that will make the main argument.
% Beautiful polished sentences will be formed only afte we agree on these basic things
\section{Introduction}
Cation interactions with cellular membranes play a key role in several biological processes,
like in signal propagation in neurons and vesicle fusion.
Cation interactions with lipid bilayers serving as a model for cellular
membranes are thus widely studied with experimental \cite{cevc90,tocanne90,binder02,pabst07,uhrikova08}
and theoretical methods \cite{Berkowitz12,??}. General conclusion from experimental
studies has been that multivalent ions and lithium have weak specific binding in
phopholipid bilayers, while other monovalent ions do not essentially
bind \cite{cevc90,tocanne90,seelig90,binder02}. The presence of anoinic lipids, like PS or PG,
increase the concentration close to the bilayer and thus the amount of bound
ions, but do not affect the specific binding constant \cite{seelig90}.
The binding details, like binding sites and stoichiometry are not yet fully
resolved but interpretation of NMR and scattering experiments suggest that one
Ca2+ interacts mainly with the choline groups \cite{hauser76,hauser78,herbette84} of two
phospholipid molecules \cite{altenbach84}.

Classical molecular dynamics simulations have potential to solve the ion binding details
in lipid bilayers and reveal its relevance to various biological
problems \cite{bockmann03,bockmann04,??}. However, the available
molecular dynamics simulation models have a strong tendency to overestimate
cation binding on zwitterionic bilayers and none of them can reproduce the
experimental data with the accuracy required for the interpretation of
experiments \cite{catte16}. The overestimated specific cation binding also
makes zwitterionic bilayers effectively positively charged, which could
potentially lead to significant artefacts in applications.
Thus, there is a vast demand for classical molecular dynamics simulation
model which correctly reproduces cation binding in lipid bilayers.

The lack of electronic polarizability from the classical MD simulation
models is a potential source of artefact, which could lead to overbinding
of cations. 
%Almost all lipid bilayer simulations reported in the literature 
%are done with force fields that represent interactions between atoms
%with pairwise additive empirical potential and exclude the electronic 
%polarizability \cite{SOME_review, FF_papers}.
The issue has been considered higly relevant since the early days of
lipid bilayer simulations and pioneering simulation studies scaled
the partial charges to effectively include electronic
polarizability \cite{jonsson86,egberts94}. The explicit inclusion of
electronic polarizability has been, however, turned to be 
practically complicated and implementations for lipids are rare \cite{chowdhary13}.

In this work we show that the cation overbinding in classical MD simulations
can be corrected by including electronic polarizability by using effective continuum
correction (ECC)~\cite{leontyev11} for polar region of zwitterionic lipid molecules.
This is essentially physicalle well justified version of partial charge scaling
implemented in early days of lipid and surfctant simulations \cite{jonsson86,egberts94}. 
The approach has been previously shown in to improve bulk performace of
ion models against neutron scattering data \cite{Jungwirth2015,kohagen14,kohagen16}.
The better bulk behaviour was not, however, sufficient to correct binding in lipid
bilayers \cite{catte16}. 
%motivation for its application to zwitterionic lipids like POPC.

@@

\subsection{Lipid bilayers without ions}
The scattering form factors, NMR order parameters and area per lipids calculated from 
the ECC corrected lipid model for POPC are compared to experiments and original
Lipid14 results in Fig. \ref{simVSexpNOions} and in Table~\ref{tab:apls}. 
%The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
%by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.
The structural quality is comparable to the state of art lipid models available in literature \cite{ollila16},
thus we conclude that the ECC corrected lipid model reproduces the lipid bilayer structure
in liquid disordered phase with similar accuracy than other available models
\todo{Discussion to be finished when we have all the results in the figure}.
\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
%  \caption{\label{fig:form-f}
%    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
%\end{figure}
%
%\begin{figure}[]
%  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and EECLipid17 models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure}
  \todo{Should we add the results from original lipid14?}
\end{figure}
%Area per molecules extracted from MD simulations and SPD model fitted to scattering data \todo{check that this the case for the used values}
%are shown in Table \ref{tab:apls}.
\todo{finalize figure (NMR headgr. OPs + SAXS, continue in the discussion.}
\begin{table}
  \caption{Area per lipid from different models for POPC without ions\label{tab:apls} }
  \begin{tabular}{c c c}
    model          & A (Å$^2$)   & Temperature [K] \\
    \hline
    Lipid14 (literature)  & 65.6$\pm$ 0.5  &  303 \\
    Lipid14ecc0.80+sigma0.875 &        &  313    \\
    GMX small patch           & 64.9   &         \\
    GMX 4xbig patch           & 65.5   &         \\
    oMM small patch           & 63.65  &         \\
    oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment \cite{Jambeck2012}\todoii{REF}{put original references, not Slipids param. paper.}  & 62.7  &  293    \\
    experiment  & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}

Headgroup order parameter response to bound charge was evaluated against
experimental data measured with cationic surfactant
(dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$) \cite{scherer89}.
The exact amount of bound charge in the membrane is known these systems, because
practically all cationic surfactant molecules are embedded in lipid bilayer due to
their amphiphilic nature. Thus, the headgroup order parameter changes as a function of
mole fraction of cationic surfactants in  Fig. \ref{OrderParameterCHANGESnewMODELS} gives
also the order parameter changes as a function of bound cations.
\todo{I think that we should make a separate figures for this one and ion concentrations.
  In the current figure it would be difficult to show this with a reasonable scale.
  Currently Lipid14 results are cut out, thus the scale should be increased.
  This would, however, make the changes with CaCl too small.
  The change of headgroup tilt could be incorporated in the same figure with order parameter
  response to cationic surfactant.
}
The headgroup order parameter response to bound cation concentration
is approximately linear up to $\sim$0.3 mole fraction in experiments \cite{scherer89}.
The linearity is also observed in simulations with original Lipid14 and with ECC correction.
%from experiments \cite{seelig87} and simulations with Lipid14 model and with ECC-lipids model 
%as a function of bound charge are shown in
Quantitative comparison, however, reveals that the response is overestimated in 
original Lipid14 for both segments, while the ECC corrected model gives a
good agreement for the change of $\alpha$ segment order parameter, but slightly
underestimates the $\beta$ segment order parameter change.
The overestimation of order parameter changes with original Lipid14 model 
suggests that the overestimated response with CaCl$_2$ concentration in \cite{catte16} 
can be partly explained by the high sensitivity of the headgroup order parameter response
to bound charge.

Secondly, the $S^\alpha/S^\beta$ ratio of the response is found to be slightly larger than in 
experiments (VALexp vs VALsim
\todo{Add values of $S^\alpha/S^\beta$ response for sim and experiment
  SAMULI: Maybe these could be put in the same figure with the order parameter
  response and P-N vector angle change with surfactants.
}
).
This property is kept also by the newly derived model, ECC-lipid, and, hence, 
it shows a perfect agreement in the response of the headgroup order parameter $S^\alpha$ 
but underestimates slightly the response of $S^\beta$.

@@

Headgroup order parameter response to increasing CaCl$_2$ concentration
from experiments, original Lipid14 model and ECC corrected model are shown
in Fig. \ref{OrderParameterCHANGESnewMODELS}. The order parameter response
is significantly overestimated in original Lipid14 model, while results from
ECC corrected model are in good agreement with experiments.
This is a significant improvement over previously available models,
which always overstimate the order parameter response to CaCl$_2$
concentration \cite{catte16}. The good agreement with experiments indicate
that the binding details of Ca2+ are realistic in the ECC corrected model
and it can be thus used to study lipid-ion interaction details.

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2_surf.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of NaCl, CaCl$_2$ concentration and
    cationic surfactant (dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$)
    from simulations and experiments (DPPC \cite{akutsu81}, POPC \cite{altenbach84}, surfactant \cite{scherer89}).
    Simulations with Lipid14 and Åqvist ion model from \cite{catte16,lipid14POPC0mMNaClfiles,lipid14POPC350mMCaClfiles,lipid14POPC1000mMCaClfiles}.
  }
  \todo{Add Lipid14-Aquist data.
    Lipid14/Åqvist data to be added from https://github.com/NMRLipids/lipid\_ionINTERACTION/blob/master/Data/POPC/CaCl/LIPID14/LIPID14caclCONSchange.dat.
    Joe: I'm not sure what is meant -- I think Aquist data are actually plotted there. I recently changed it to L14+Dang ions (both data and plot).
    I think just one ion model is sufficient (and ECC-ions are based on Dang model).
    Samuli: I think that we could add also the Aqvist data. This is in the NMRlipids II publication so it might
    make easier to follow for people who have red it publication.
  }
\end{figure*}

Ion density profiles between different simulation models are compared in Fig. \ref{fig:cacl-dens}.
Density profiles from simulations with original Lipid14 and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{kohagen14,kohagen16} along with original Lipid14 does not significantly change it
\todo{If we show density profile for this, we should show also the order parameter changes}.
The new ECC-lipid model with scaled ions exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
This demonstrates that cation binding in zwitterionic phospholipid bilayer can be accurately
described with classical MD simulation model with effective included of electronic polarizability.

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Aquist parameters
    and with ECC ions and ECCLipids17 with ECC ions. }
  \todo{We should add the location of bilayer here somehow.
    In NMRlipids II the location of phosphate was shown with green vertical line.}
  \todo{I would add Aqvist data from NMRlipids II in here as well.}
\end{figure}

@@
